%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Abhay}{Ashok Kumar}{ Software Developer| +91-9042314857 | \href{a.abhay96@gmail.com}{a.abhay96@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Erlang \textbullet{}   C \textbullet{} C++\\ 
\location{Over 1000 lines:}
MySQL \textbullet{} Oracle \textbullet{} C \# \textbullet{} Unity \textbullet{} Unreal Engine \\
\location{Familiar:}
 \textbullet{} JavaScript \textbullet{} Python
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/SSJAbatron}{\bf ssjabatron} \\
LinkedIn://  \href{https://www.linkedin.com/in/abhay-ashok-kumar-7b685bb3}{\bf Abhay Ashok Kumar} \\
Code Wars(Competitive Programming)://  \href{https://www.codewars.com/users/SSJAbatron}{\bf ssjabatron} \\
LeetCode(Competitive Programming)://  \href{https://leetcode.com/SSJAbatron/}{\bf ssjabatron} \\
itch.io(Game Projects)://  \href{https://ssjabatron.itch.io}{\bf ssjabatron}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Jerusalem College Of Engineering}
\descript{BE in Computer Science}
\location{April 2014 | Chennai, Tamil Nadu, India}
\location{ Cum. GPA: 8.23 / 10}
%Major GPA: 3.9 / 4.0
\sectionsep

\subsection{D.A.V Senior Secondary School}
\location{Grad. May 2014|  Chennai,Tamil Nadu, India}
\location{Percentage: 89\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
November 2023 |{\bf 14\textsuperscript{th}/21} Trijam 246(Game Jam), itch.io\\
November 2023 |{\bf 3\textsuperscript{rd}/23}  Trijam 245(Game Jam), itch.io\\
November 2023 |{\bf 22\textsuperscript{nd}/37} Trijam 244(Game Jam), itch.io\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Odyssey Technologies Ltd.}
\descript{| Lead Programmer }
\location{May 2023 - Present | Onsite - Chennai, Tamil Nadu, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Technologies used: C, C\#.
\item Working on PAMs(Pluggable Authentication Modules) to build a custom authentication module in C to support protocols such as SMTP, IMAP/POP3.
\item Built a C\# library that computes JWS using Native Cryptography functions for .NET applications.
\end{tightemize}
\sectionsep

\runsubsection{Gamer2Maker}
\descript{| Game Designer(Apprenticeship)}
\location{April 2023 – Present | Remote - Chennai, Tamil Nadu, India}
\begin{tightemize}
\item Technologies Used: Power Point, Unity, Asperite, GitHub, C\#
\item Working on Top-Down 2d Pixel art Action Arcade Game in a team of 6.
\item Project Repository: \textbf{\href{https://github.com/tarun-medida/FindTheDragonOrbs}{Find the Dragon Orbs}}
\end{tightemize}
\sectionsep

\runsubsection{Odyssey Technologies Ltd.}
\descript{| Deputy Lead Programmer}
\location{July 2021 – April 2023 | Onsite - Chennai, Tamil Nadu, India}
\begin{tightemize}\item Technologies used: Erlang, C, C++, Oracle.
\item Built a tool that uploads application reports using SFTP and supported SFTP authentication methods: password, key, password and key(Erlang SFTP library).
\item Built a request limiter with a configuration to support the configured Requests per second across the entire server or separate configurations for applications enrolled to the server.
\end{tightemize}
\sectionsep

\runsubsection{Odyssey Technologies Ltd.}
\descript{| Junior Programmer}
\location{July 2019 – June 2021 | Onsite - Chennai, Tamil Nadu, India}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Technologies used: Erlang, C, C++, Oracle.
\item Implemented a Server that exposes APIs for storing and retrieving data from a database. Implemented JSON APIs and server implementation using MochiWeb Erlang Library.
\item Improved the working of a directory crawler tool that parses files of various extensions, browser and OS key stores and uploads the formatted data to a server configured in the tool, written in C and C++.
\end{tightemize}
\sectionsep

\runsubsection{Odyssey Technologies Ltd.}
\descript{| Trainee Engineer}
\location{June 2018 – June 2019 | Onsite - Chennai, Tamil Nadu, India}
\begin{tightemize}
\item Technologies used: Erlang
\item  Writing small code snippets to make tools for parsing complex data in Erlang.\end{tightemize}
\sectionsep

\runsubsection{Trooze}
\descript{| Front End Developer Intern}
\location{July 2017 – October 2017 | Remote - Chennai, Tamil Nadu, India}
\begin{tightemize}
\item Worked with HTML, CSS, JavaScript to build website homepage.\end{tightemize}
\sectionsep
\end{minipage} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\end{document}  \documentclass[]{article}